---
title: "AWS Database"
author: "Davis Vaughan"
date: "2/7/2017"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(DBI)
library(tidyquant)
library(dplyr)
```

Connect to amazon web services using the DBI package.

```{r}
cn <- dbConnect(drv = RMySQL::MySQL(), 
                username = "user1", 
                password = "testpassword", 
                host = "davisdbinstance.crarljboc8to.us-west-2.rds.amazonaws.com", 
                port = 3306, 
                dbname = "firstdb")
```

Download stock data using `tidyquant`.

```{r}
aapl <- tq_get("AAPL")
```

Write the tibble to the database using DBI. 

- Already done, don't run again.
- User only has SELECT privelages anyways.


```{r}
#dbWriteTable(cn, "apple", aapl)
```

Pull it back down using SQL in RMarkdown! 

- Note that dates did get converted to chr.
- Only pulls first 1000 rows.

```{sql connection=cn}
SELECT * 
FROM apple;
```

Pull it back down using the DBI package in R! 

- Pulls all rows.

```{r}
x <- dbGetQuery(cn, "SELECT * FROM apple;")

head(x)
```

Make sure and disconnect so we can try other things.

```{r }
dbDisconnect(cn)
```


Now, redo the connection but use dplyr!

```{r}
cn <- src_mysql(user = "user1", password = "testpassword", host = "davisdbinstance.crarljboc8to.us-west-2.rds.amazonaws.com", port = 3306, dbname = "firstdb")
```

Select the apple table from that database. This does not actually pull in the data. Just makes the connection!

```{r}
apple_table <- tbl(cn, "apple")
```

We can use almost any dplyr command with this! It queries the database, and does not do the manipulation in R. This is insane.

```{r}
apple_table %>% select(date, adjusted)
```

A dplyr `filter()`.

```{r}
apple_table %>% filter(date < "2008-01-01")
```

IBM added to the database using `copy_to()`. 

- Dont run this either, already done.

```{r}
#ibm <- tq_get("IBM")

#copy_to(cn, ibm, temporary = FALSE)
```

Pull down IBM, then mutate it to add daily returns using `tidyquant`.

```{r}
ibm_table <- tbl(cn, "ibm")
real_tibble <- collect(ibm_table)
real_tibble$date <- as.Date(real_tibble$date)

real_tibble <- real_tibble %>% 
  tq_mutate(ohlc_fun = Ad, 
            mutate_fun = periodReturn, 
            period = "daily")

head(real_tibble)
```



